Pruning Subsequence Search with Attention-Based Embedding

### 2015-09-24 paper.tex
Add qualitative figure

@@

>>>>

\begin{figure*}[htb!]
  \centering
  \includegraphics[width=\textwidth]{embeddings.pdf}
  \caption{Embeddings for two pairs of matching sequences from our best-performing system.  The first two rows display pairs of matching constant-Q spectrograms.  For both pairs, the right sequence is a subsequence of the left.  The last two rows show their resulting embeddings.  Dashed arrows denote which embedding corresponds to which sequence.}
  \label{fig:embeddings}
\end{figure*}

@@

Some qualitative intuition about our system's behavior can be gained by inspecting the embeddings resulting from matching and non-matching pairs of sequences.
Embeddings for two different matching sequence pairs from the validation set can be seen in Figure \ref{fig:embeddings}.
Among the four embeddings displayed, the pairs of matched embeddings resulted in Euclidean distances of 0.159 and 0.347, while non-matching pairs had distances of 1.08 and 1.15.
While these distances indicate the appropriate behavior, there are nevertheless some noticeable discrepancies between the embeddings of the matched sequences.
